\documentclass{article}
\usepackage{fullpage}
\usepackage{latexml}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}

\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\cov}{cov}
\newcommand{\deq}{\overset{\scriptscriptstyle{d}}{=}}

\newcommand{\given}{\,\vert\,}
\newcommand{\st}{\,\colon\,} % such that
\newcommand{\floor}[1]{{\left\lfloor #1 \right\rfloor }}
\newcommand{\one}{\mathbb{1}}

\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{exercise}{Exercise}

\catcode`\_=11\relax
\newcommand\email[1]{\_email #1\q_nil}
\def\_email#1@#2\q_nil{%
  \href{mailto:#1@#2}
    {{\emailfont\detokenize{#1}\emailampersat\detokenize{#2}}}%
}
\newcommand\emailfont{\rmfamily}
\newcommand\emailampersat{{\small@}}
\catcode`\_=8\relax 

\begin{document}

\title{Open Digital Mathematics Library}

\maketitle

\section{ODML use cases}

Some use cases for the ODML for different stakeholder groups (, teacher, researcher, administrator, advocate, and accreditor)\footnote{Adapted from Corneli and Mikroyannidis, 2012 ``\href{http://oro.open.ac.uk/33221/1/corneli_chap_okada_book.pdf}{Crowdsourcing Education: A Role-Based Analysis}''}:

\begin{enumerate}
\renewcommand{\theenumi}{\Roman{enumi}}
\item\label{student} (\textbf{Student}) I go to class, we do a class project, the various aspects of which are things I can add to my portfolio or work-record; and fundamentally it's all about gaining a skill.  \emph{The ODML is helpful for me because it connects me with high-quality, low-cost learning resources that are personalized to my current skill set and learning goals.} 
\item\label{teacher} (\textbf{Teacher}) I lead a class, we plan and implement the curriculum, my work involves giving lectures and feedback and, more infrequently, meetings with my colleagues; and fundamentally it's all about helping my students. \emph{The ODML is helpful for me because it helps me find and review high-quality, low-cost learning resources, connecting with other classrooms around the world.}
\item\label{researcher} (\textbf{Researcher}) I ask a thought-provoking question, we discuss or experiment, the results are written up in papers; and fundamentally it's all about generating new knowledge. \emph{The ODML is helpful for me because it helps me find relevant readings and rapidly build knowledge in new research areas, integrates useful computational tools, helps me share my research and discuss the publications of others.}
\item\label{administrator} (\textbf{Administrator}) I transform ideas into code or policies, we collectively manage a body of work, the pieces are the components of a functioning system; and fundamentally it's all about creating a workflow that works.  \emph{The ODML is helpful for me because it means that we don't have to develop everything in-house: we can contribute to a high-quality shared open source resource that is customizable to the needs of our organization.}
\item\label{advocate} (\textbf{Advocate}) I engage in dialog, where I promote a certain position, we try to find common ground, the results of various interactions and transactions are assembled into strategies; and fundamentally it's all about creating a distinctive organizational identity and strong partnerships. \emph{The ODML is helpful for me because the organization lets me advance the projects of the particular constituencies I serve transparently, getting feedback and help from other parties working in closely related areas.}
\item\label{accreditor} (\textbf{Accreditor}) I endeavor to discern societal needs, we work to achieve a rough consensus with a larger body of stakeholders, the results describe a certain clearly-defined skill set; and fundamentally it's all about knowing the appropriateness and relevance of a certain training process. \emph{The ODML is helpful for me because it serves the whole field of mathematics and mathematical science.}
\end{enumerate}

\section{ODML focal areas}

We are interested in research and development in the following areas:

\begin{enumerate}
\renewcommand{\theenumi}{\Alph{enumi}}
\item\label{ontology} an ontology for mathematics (or, for a start, a mathematical wordnet) (\href{https://github.com/holtzermann17/skelodml/wiki/A.-An-ontology-for-mathematics}{discuss})
\item\label{encoding} a semantically meaningful encoding of mathematical definitions, theorems, formulas, lemmas, \&c. (\href{https://github.com/holtzermann17/skelodml/wiki/B.-Semantically-meaningful-encodings-of-mathematical-objects}{discuss})
\item\label{search} semantic mathematical search (\href{https://github.com/holtzermann17/skelodml/wiki/C.-Semantic-mathematical-search}{discuss})
\item\label{fingerprinting} \href{http://www.ams.org/notices/201308/rnoti-p1034.pdf}{fingerprinting of mathematical theorems} (\href{https://github.com/holtzermann17/skelodml/wiki/D.-Fingerprinting-of-mathematical-theorems}{discuss})
\item\label{proof} tools for assisting mathematical proof based on semantically encoded mathematics (\href{https://github.com/holtzermann17/skelodml/wiki/E.-Tools-for-assisting-mathematical-proof}{discuss})
\item\label{tagging} manual and computerized (machine-learning based) tagging of mathematical papers (\href{https://github.com/holtzermann17/skelodml/wiki/F.-(semi)automated-tagging-of-mathematical-papers}{discuss})
\item\label{annotation} annotation tools for PDF files and scanned papers (\href{https://github.com/holtzermann17/skelodml/wiki/G.-annotation-tools-for-PDF-files}{discuss})
\item\label{authoring} support for open semantic docs and authoring workflows: (X)HTML, Kohlhase's stex, etc. (\href{https://github.com/holtzermann17/skelodml/wiki/H.-Open-semantic-docs-and-authoring-workflows}{discuss})
\item\label{community} community/authority management like mathoverflow, for management and production of collections (\href{https://github.com/holtzermann17/skelodml/wiki/I.-community-and-authority-management-tools}{discuss})
\item\label{data} structured data management tools: integration with Zotero, BibServer and other tools (\href{https://github.com/holtzermann17/skelodml/wiki/J.-structured-data-management-tools}{discuss})
\item\label{ocr} OCR for mathematics (\href{https://github.com/holtzermann17/skelodml/wiki/K.-OCR-for-mathematics}{discuss})
\end{enumerate}

\section{ODML Organization}

We propose to offer:

\begin{enumerate}
\item\label{integration} a light-weight integration and organizational layer for coordinating work on the topics listed above (\href{https://github.com/holtzermann17/skelodml/wiki/1.-Home}{discuss})
\item\label{mail} an index of mailing lists relevant to the effort (\href{https://github.com/holtzermann17/skelodml/wiki/2.-Mailing-lists}{discuss})
\item\label{technology} An overview of relevant technologies (\href{https://github.com/holtzermann17/skelodml/wiki/3.-Technology-overview}{discuss})
\item\label{content} An overview of relevant sources of content (\href{https://github.com/holtzermann17/skelodml/wiki/4.-Content-overview}{discuss})
\end{enumerate}

\section{Background}

This site is being created as a response to the  \href{http://www.mathunion.org/fileadmin/CEIC/planning_wdml.pdf}{forthcoming article} and
 \href{http://arxiv.org/abs/1404.1905}{recent report} from Jim Pitman and collaborators about an Open Digital Mathematics Library (ODML).
%
The site is written with skelml, a simple tool that has recently been developed to use Github together with \LaTeX ML.  This model provides a nice, neutral, supported, and standards-compliant place to collaborate.  To join, please visit, and fork, \url{https://github.com/holtzermann17/skelodml} and send us pull requests.  You can also edit the \href{https://github.com/holtzermann17/skelodml/wiki}{wiki} or
submit \href{https://github.com/holtzermann17/skelodml/issues}{issues} directly.

\section{Plans}

We will try to describe the state of the art for items \ref{ontology}--\ref{ocr}, and check whether this list of focal areas is complete (it probably is not).  Once we know that we have a reasonable outline, we can look at the division of work.  Often, small subsets of projects may fit together into a grant proposal.  For example, items \ref{annotation}, \ref{authoring} and \ref{ocr} might fit naturally together, if we want to have annotated versions of legacy documents that correspond on a line-by-line basis to open docs on the web.

\section{Example}

To illustrate the sort of thing that can be usefully stored in this repository, we've added a document with \href{http://holtzermann17.github.io/skelodml/bibserver-setup.html}{instructions} for installing BibServer, one of the relevant technologies.  Eventually, this repository will contain many similar how-tos and useful pointers to tools and content.

\end{document}
